---
title: "p8105_hw1_yw4854"
author: "Yuxuan Wang"
date: "2026-09-26"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

# Problem 1

The dataset contains data on adult penguins across `r length(levels(penguins$species))` species in the Palmer Archipelago, Antarctica.
The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

Important variables:

- `species`: Penguin species (`r levels(penguins$species)`)

- `island`: Penguin Habitat (`r levels(penguins$island)`)

- `bill_length_mm`: bill length (millimeters) 

- `bill_depth_mm`: bill depth (millimeters)

- `flipper_length_mm`: flipper length (millimeters)

- `body_mass_g`: body mass (grams)

- `sex`: penguin sex (`r levels(penguins$sex)`)

- `year`: study year

the mean flipper length:
`r mean(penguins$flipper_length_mm, na.rm = TRUE)`

### scatterplot:

```{r, warning=FALSE}
penguin_plot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
  title = "Flipper length vs Bill length",
  x = "Bill length (mm)",
  y = "Flipper length (mm)",
  color = "species"
)

penguin_plot

ggsave("scatter_plot.png", penguin_plot)
```

# Problem 2
### data frame
```{r, warning=FALSE}
set.seed(1234)

hw1_df <- tibble(norm_samp = rnorm(10), norm_greater_0 = norm_samp > 0, char_vec = c("Westie", "Golden Retriever", "Labrador Retriever", "Beagle", "Poodle", "Husky", "Boxer", "Samoyed", "French Bulldog", "Yorkshire Terrier"), factor_vec = factor(rep(c("friendly", "energetic", "calm"), length.out = 10))
)

hw1_df
```
### mean of each variable

```{r, warning=FALSE}
mean(pull(hw1_df, norm_samp))

mean(pull(hw1_df, norm_greater_0))

mean(pull(hw1_df, char_vec))

mean(pull(hw1_df, factor_vec))
```

- mean of norm_samp works.Because it is numeric.
- mean of norm_greater_0 works. Because it is logical.
- mean of char_vec doesn't work. Because is not numeric or logical.
- mean of factor_vec doesn't work. Because is not numeric or logical.

### convert variables from one type to another
```{r, eval=FALSE}
as.numeric(pull(hw1_df, norm_greater_0))
as.numeric(pull(hw1_df, char_vec))
as.numeric(pull(hw1_df, factor_vec))
```
- norm_greater_0 convert to 1 and 0. This can explain why mean() succeeded. Because 0 and 1 are number. For example 0.4 means there are 4 variable greater than 0.

- char_vec convert to NA, because words cannot be parsed into numbers.

- factor_vec convert to 1,2 and 3. Because 1,2 and 3 are categorical labels, they have no meaning in terms of the mean.
