---
title: "p8105_hw1_yw4854"
author: "Yuxuan Wang"
date: "2026-09-26"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

# Problem 1

The dataset contains data on adult penguins across `r length(levels(penguins$species))` species in the Palmer Archipelago, Antarctica.
The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

Important variables：

- `Species`: Penguin species (`r levels(penguins$species)`)

- `Island`: Penguin Habitat (`r levels(penguins$island)`)

- `bill_length_mm`: bill length (millimeters) 

- `bill_depth_mm`: bill depth (millimeters)

- `flipper_length_mm`: flipper length (millimeters)

- `body_mass_g`: body mass (grams)

- `sex`: penguin sex (`r levels(penguins$sex)`)

- `year`: study year

the mean flipper length:
`r mean(penguins$flipper_length_mm, na.rm = TRUE)`

### scatterplot:

```{r, warning=FALSE}
penguin_plot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
  title = "Flipper length vs Bill length",
  x = "Bill length (mm)",
  y = "Flipper length (mm)",
  color = "species"
)

penguin_plot

ggsave("scatter_plot.png", penguin_plot)